Neighbor-Based Decentralized Training Strategies for Multi-Agent Reinforcement Learning

### 2024-10-02 paper-2024-sac-marl-neighbouring-strategies.tex
reduce the domain

\section{Introduction}

Distributed artificial intelligence has emerged as a prominent research area in recent years, 
evolving from its roots in multi-agent systems engineering 
through advancements in distributed learning. 
%
This evolution has encompassed collective behavior learning (e.g., COIN) 
and culminated in the modern field of multi-agent deep reinforcement learning (MADRL). 
%
MADRL has gained significant traction due to its flexibility and capacity to learn diverse behaviors, 
ranging from cooperative to competitive, 
as demonstrated in various case studies involving video games, swarm robotics, 
and traffic management. 
%
This paper focuses on the subdomain of cooperative multi-agent reinforcement learning, 
a particularly active and impactful area of research within MADRL.

>>>>

\section{Introduction}
The increasing complexity of real-world systems, from robotic swarms to smart grids, demands intelligent control strategies capable of adapting to dynamic and often unpredictable environments.
In this direction, reinforcement learning (RL) has emerged as a powerful paradigm for training agents to interact with their environment and learn optimal policies through trial and error.
%
Moving beyond single-agent settings, multi-agent reinforcement learning (MARL) extends RL to scenarios where multiple agents must collaborate or compete to achieve a common goal.
%
Recent advances in deep learning have further revolutionized the field, enabling the training of complex policies in high-dimensional state and action spaces, leading to the emergence of multi-agent deep reinforcement learning (MADRL).
%
MADRL has gained significant traction due to its flexibility and capacity to learn diverse behaviors, 
ranging from cooperative to competitive, 
as demonstrated in various case studies involving video games, robotics,
and traffic management. 
%
This paper focuses on the subdomain of cooperative multi-agent reinforcement learning, 
a particularly active and impactful area of research within MADRL.
